### 2024-02-29 manuscript.tex
Changed description of rate PCA axis from acidic to charged to better describe constituent features

The first two principal components of the root distributions show little overall structure, though there is a slight enrichment of regions along two axes that correlate with acidic and polar features, respectively (\ref{sfig:root}~Fig). Likewise, the projections of the rates onto the first two principal components are largely distributed along the first (Fig~\ref{fig:rate}A). This observation and the variable amounts of sequence divergence in the regions led us to suspect the first principal component was a measure of the overall rate of sequence evolution. Plotting the first principal component against the sum of the average amino acid and indel rates as measured by substitution models revealed a strong association (Fig~\ref{fig:rate}B). We then projected the rates along second and third principal components to determine if these higher order components contained any additional structure. The resulting distribution is roughly triangular and contains three major axes of variation, corresponding to rapid changes in the regions' proportions of acidic, glutamine, and glycine residues (Fig~\ref{fig:rate}C-D). Inspection of regions selected along these axes confirmed the high rates of evolution of these features (Fig~\ref{fig:rate}E-G). Furthermore, we observe a similar distribution when the rates of the order regions were projected along their second and third principal components, which suggests a lack of constraint along these axes is a general property of rapidly evolving proteins (\ref{sfig:order}~Fig).

>>>>

The first two principal components of the root distributions show little overall structure, though there is a slight enrichment of regions along two axes that correlate with acidic and polar features, respectively (\ref{sfig:root}~Fig). Likewise, the projections of the rates onto the first two principal components are largely distributed along the first (Fig~\ref{fig:rate}A). This observation and the variable amounts of sequence divergence in the regions led us to suspect the first principal component was a measure of the overall rate of sequence evolution. Plotting the first principal component against the sum of the average amino acid and indel rates as measured by substitution models revealed a strong association (Fig~\ref{fig:rate}B). We then projected the rates along second and third principal components to determine if these higher order components contained any additional structure. The resulting distribution is roughly triangular and contains three major axes of variation, corresponding to rapid changes in the regions' proportions of glutamine, charged, and glycine residues (Fig~\ref{fig:rate}C-D). Inspection of regions selected along these axes confirmed the high rates of evolution of these features (Fig~\ref{fig:rate}E-G). Furthermore, we observe a similar distribution when the rates of the order regions were projected along their second and third principal components, which suggests a lack of constraint along these axes is a general property of rapidly evolving proteins (\ref{sfig:order}~Fig).
